Aracna: An Open-Source Quadruped Platform for Evolutionary Robotics

### 2012-06-01 paper_aimsa/results.tex
results.tex

The results for the gaits evolved by RL\_POWER are shown in Figure 8
and Table 2. A total of 900 evaluations were performed for HyperNEAT
(300 in each of three runs). Overall the RL\_POWER gaits were the
faster and more stable by far, beating the HyperNEAT when comparing
either average or best gaits

(pic)RL\_POWER AND HyperNEAT performance chart

or best gaits. We believe that this is because RL\_POWER uses evolvable splines to represent gaits As explained earlier,  
The single best gait found during this study had a speed of

XXXX body lengths/minute, XX\%

>>>>

The results for the gaits evolved by RL PoWER are shown in Figure 8
and Table 2. A total of 900 evaluations were performed for HyperNEAT
(300 in each of three runs). Overall the RL PoWER gaits were the
faster and more stable by far, beating the HyperNEAT when comparing
either average or best gaits.

(pic)RL POWER AND HyperNEAT performance chart

We believe that this is because RL PoWER uses evolvable splines to represent gaits As explained earlier,  
The single best gait found during this study had a speed of

11.0855923766 centimeters/sec, XX\%
